---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

I watched the video with **Cem Vardar** was the guest.

Cem Vardar, an industrial engineer holding both a bachelor’s degree and a doctorate from Arizona State University, began his career at Intel before moving into data science at Carvana. His expertise lies in leveraging data-driven insights to enhance the efficiency of complex systems and to improve logistics, profitability, and sales outcomes. He uses funnel analysis to refine the customer experience by tracking their journey from initial contact to purchase, and net lift modeling to assess the effectiveness of marketing campaigns in reaching target audiences. Vardar highlights the significance of analytical skills, the value of internships, and the growing impact of artificial intelligence and entrepreneurship within industrial engineering.

1\. **Which of the following is not a field where operations research and data science are commonly applied together?**

a\) Logistic Planning

b\) Production Planning

c\) Inventory Management

d\) Customer Relationship Management

*Answer: d*

2\. **How does funnel analysis benefit businesses, and why is it valuable?**

*Answer: Funnel analysis monitors the path of potential customers from their first interaction to the final purchase. It enables businesses to comprehend and enhance each phase of the customer experience, ultimately leading to improved conversion rates.*

## (b)

First, we load the *dslabs* library and retrieve the *polls_us_election_2016* dataset from it.

```{r}
library(dslabs)
data(polls_us_election_2016)
```

Display the first 10 rows of the data

```{r}
head(polls_us_election_2016, 10)
```

```         
```

Calculate the total number of missing values NA rephrase

```{r}
total_number_of_NA <- sum(is.na(polls_us_election_2016))
print(total_number_of_NA)
```

```         
```

Create variables for my birth year and first name, define a function to replace missing values, apply this function to each column of the dataset to fill in missing values, assign the updated data to a new variable, calculate the total number of missing values in the updated dataset, and print the count of missing values in the modified data.

```{r}
my_birth_year <- 2002
my_first_name <- "Enis"

change_na_values <- function(x) {
  if (is.numeric(x)) {
    return(ifelse(is.na(x), my_birth_year, x))  
  } else {
    return(ifelse(is.na(x), my_first_name, x))
  }
}

polls_us_election_2016 <- as.data.frame(lapply(polls_us_election_2016, change_na_values))

changed_data <- polls_us_election_2016

total_number_of_na_for_changed <- sum(is.na(changed_data))
print(total_number_of_na_for_changed)
```

```         
```

Show the first 10 rows of the modified dataset.

```{r}
head(changed_data, 10)
```

```         
```
